Technical Dimensions of Programming Systems

### 2022-09-22 prog-2022/prog22-master.tex
Reinclude appendix in main and final minor changes

% Class scrartcl Warning: seems someone has broken package `auxhook'.
% Usually this happens, if `auxhook' is loaded or used implicitly or explicitly
% by patching \document or via etoolbox command \AtEndPreamble. Trying an
% emergency workaround. You can avoid this warning adding:
\usepackage{auxhook}
% before \begin{document} on input line 6.
\usepackage{changepage} % For the single-page summary table PDF insert.
\usepackage{pdfpages}
\usepackage{pifont} % For checkmark / cross symbols for Appendix table :)

@@

NOTE TO REVIEWERS: The main contribution of the paper is a comprehensive survey of 22 design dimensions of programming systems. Each one comes with detailed discussion, including known uses, to properly motivate it. Regrettably, we only have space for a small number of these dimensions in the main paper body. To give a broader picture of what we are contributing, we invite the reader to explore Appendix\ \ref{dimensions-catalogue} for dimensions that suit their interest.
\end{abstract}

@@

\newcommand{\joel}[1]{}
\newcommand{\note}[1]{}
\newcommand{\tp}[1]{}
\newcommand{\mybox}[1]{\noindent\fbox{\parbox{\textwidth}{#1}}}
\providecommand{\tightlist}{}% Don't want Pandoc's tight lists
%\newcommand{\hypertarget}[1]{}

>>>>

% Class scrartcl Warning: seems someone has broken package `auxhook'.
% Usually this happens, if `auxhook' is loaded or used implicitly or explicitly
% by patching \document or via etoolbox command \AtEndPreamble. Trying an
% emergency workaround. You can avoid this warning adding:
\usepackage{auxhook}
% before \begin{document} on input line 6.
\usepackage{changepage} % For the single-page summary table PDF insert.
\usepackage{pdfpages}
\usepackage{pifont} % For checkmark / cross symbols for Appendix table :)
\usepackage{amsthm} % For numberless Definition
\usepackage{epigraph} % For the opening quotes

@@

NOTE TO REVIEWERS: The main contribution of the paper is a comprehensive catalogue of 22 design dimensions of programming systems. Each one comes with detailed discussion, including known uses, to properly motivate it. We feel these belong in the main paper body rather than in an appendix, even though this increases the page count, and have received permission to do this. We intend the catalogue as a reference to be used \emph{as necessary,} not to be read from start to finish. This means that Section\ \ref{technical-dimensions-catalogue} can be considered to be \textbf{outside} of the normal reviewable material, leaving the rest of the paper within the journal's 22 page limit.
\end{abstract}

@@

\newcommand{\joel}[1]{}
\newcommand{\note}[1]{}
\newcommand{\tp}[1]{}
\newcommand{\mybox}[1]{\noindent\fbox{\parbox{\textwidth}{#1}}}
\providecommand{\tightlist}{}% Don't want Pandoc's tight lists
\newtheorem*{defn}{Definition}
%\newcommand{\hypertarget}[1]{}
